---
title: "Survey Analysis"
author: "Michael Spencer, Foster Docherty, Jorge Nam Song"
date: "11/14/2019"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r, include=FALSE}
## Setup

### Libraries
if (!require(tidyverse)) install.packages("tidyverse")
library(tidyverse)

if (!require(nnet)) install.packages("nnet")
library(nnet)
```

```{r, include=FALSE}
### Parameters
path_data <- "Batch_3835086_batch_results.csv"

path_pop_dist <- "https://5harad.com/mse231/assets/pop_dist.tsv"
```

```{r, include=FALSE}
### Load Data
data_raw <-
  path_data %>%
  read_csv()

data_pop_distr <-
	path_pop_dist %>% 
	read_tsv()
```

```{r, include=FALSE}
### Prep & Clean Data
old_names <- data_raw %>%
  select(starts_with("Answer.")) %>%
  colnames()

new_names <-
  str_replace_all(
    old_names,
    pattern = "Answer.|.TRUE",
    replacement = ""
  )

data <-
  data_raw %>%
  select(
    id = WorkerId,
    start = AcceptTime,
    submit = SubmitTime,
    total_time = WorkTimeInSeconds,
    starts_with("Answer.")
  ) %>%
  rename_at(vars(old_names), ~new_names) %>%
  group_by(id) %>%
  gather(
    key = "variable",
    value = "var_log",
    starts_with("age_"),
    starts_with("education_"),
    starts_with("familiarity_"),
    starts_with("race_"),
    starts_with("sex_")
  ) %>%
  arrange(id) %>%
  filter(var_log) %>%
  select(-var_log) %>%
  separate(variable, into = c("demographic", "response"), sep = "_") %>%
  spread(key = demographic, value = response) %>%
  ungroup() %>%
  mutate(
    education =
      recode(
        education,
        "no" = "no high school diploma",
        "hs" = "high school graduate",
        "coll" = "college degree",
        "pg" = "postgraduate degree"
      ),
    race =
      recode(
        race,
        "his" = "hispanic"
      ),
    education =
      factor(
        education,
        levels = c(
          "no high school diploma",
          "high school graduate",
          "college degree",
          "postgraduate degree"
        )
      ),
    familiarity = 
    	recode(
    		familiarity,
    		"none" = 0,
    		"some" = 2,
    		"very" = 4
    	)
  )

data
```

\newpage
```{r, echo=FALSE}
# Analysis
# Examine Demographics

# Sex
data %>%
  filter(attention == 4, !is.na(sex)) %>%
  count(sex) %>%
  mutate(
    sex_prop = n / sum(n)
  ) %>%
  ggplot(aes(x = sex, y = sex_prop)) +
  geom_col() +
  scale_y_continuous(
    labels = scales::percent_format(accuracy = 1)
  ) +
  theme_minimal() +
  labs(
    title = "Distribution of Respondents' Sex",
    y = "Proportion of Survey",
    x = "Sex",
    caption = "\nResponses only include those that passed our attention test."
  )

# Race
data %>%
  filter(attention == 4, !is.na(race)) %>%
  count(race) %>%
  mutate(
    race_prop = n / sum(n),
    race = str_to_title(race) %>% fct_reorder(race_prop)
  ) %>%
  ggplot(aes(x = race, y = race_prop)) +
  geom_col() +
  scale_y_continuous(
    labels = scales::percent_format(accuracy = 1)
  ) +
  theme_minimal() +
  labs(
    title = "Distribution of Respondents' Race",
    y = "Proportion of Survey",
    x = "Race/Ethnicity",
    caption = "\nResponses only include those that passed our attention test."
  )

# Education
data %>%
  filter(attention == 4, !is.na(education)) %>%
  count(education) %>%
  mutate(
    ed_prop = n / sum(n)
  ) %>%
  ggplot(aes(x = education, y = ed_prop)) +
  geom_col() +
  scale_y_continuous(
    labels = scales::percent_format(accuracy = 1)
  ) +
  theme_minimal() +
  labs(
    title = "Distribution of Respondents' Education Level",
    y = "Proportion of Survey",
    x = "Education",
    caption = "\nResponses only include those that passed our attention test."
  )

# Age
data %>%
  filter(attention == 4, !is.na(age)) %>%
  count(age) %>%
  mutate(
    age_prop = n / sum(n)
  ) %>%
  ggplot(aes(x = age, y = age_prop)) +
  geom_col() +
  scale_y_continuous(
    labels = scales::percent_format(accuracy = 1)
  ) +
  theme_minimal() +
  labs(
    title = "Distribution of Respondents' Age",
    y = "Proportion of Survey",
    x = "Age",
    caption = "\nResponses only include those that passed our attention test."
  )
```

```{r, echo=FALSE}
# Substantive Questions

# Familiarity with 311
avg_familiarity <- 
	data %>% 
	filter(attention == 4) %>% 
	pull(familiarity) %>% 
	mean(na.rm = TRUE)

# Familiarity with 311 by sex
data %>% 
	filter(attention == 4, !is.na(familiarity), !is.na(sex)) %>% 
	group_by(sex) %>% 
	summarize(avg_fam = mean(familiarity)) %>% 
	ggplot(aes(x = sex, y = avg_fam)) +
	geom_hline(yintercept = avg_familiarity, linetype = 2) +
	geom_col() +
	coord_cartesian(ylim = c(0, 4)) +
	annotate(
		"text", 
		x = "female", 
		y = avg_familiarity, 
		label = "Average Familiarity\nfor All",
		vjust = 0
	) +
	theme_minimal() +
  labs(
    title = "Average 311 Familiarity by Sex",
    y = "Average Familiarity\n(from 0-4)",
    x = "Sex",
    caption = "\nResponses only include those that passed our attention test."
  )

# Familiarity with 311 by race
data %>% 
	filter(attention == 4, !is.na(familiarity), !is.na(race)) %>% 
	group_by(race) %>% 
	summarize(avg_fam = mean(familiarity)) %>% 
	mutate(race = str_to_title(race) %>%  fct_reorder(avg_fam)) %>% 
	ggplot(aes(x = race, y = avg_fam)) +
	geom_hline(yintercept = avg_familiarity, linetype = 2) +
	geom_col() +
	coord_cartesian(ylim = c(0, 4)) +
	annotate(
		"text", 
		x = "Black", 
		y = avg_familiarity, 
		label = "Average Familiarity\nfor All"
	) +
	theme_minimal() +
  labs(
    title = "Average 311 Familiarity by Race",
    y = "Average Familiarity\n(from 0-4)",
    x = "Race",
    caption = "\nResponses only include those that passed our attention test."
  )

# Familiarity with 311 by education
data %>% 
	filter(attention == 4, !is.na(familiarity), !is.na(education)) %>% 
	group_by(education) %>% 
	summarize(avg_fam = mean(familiarity)) %>% 
	ggplot(aes(x = education, y = avg_fam)) +
	geom_hline(yintercept = avg_familiarity, linetype = 2) +
	geom_col() +
	coord_cartesian(ylim = c(0, 4)) +
	annotate(
		"text", 
		x = "high school graduate", 
		y = avg_familiarity, 
		label = "Average Familiarity\nfor All", 
	) +
	theme_minimal() +
  labs(
    title = "Average 311 Familiarity by Education",
    y = "Average Familiarity\n(from 0-4)",
    x = "Education",
    caption = "\nResponses only include those that passed our attention test."
  )

# Familiarity with 311 by age
data %>% 
	filter(attention == 4, !is.na(familiarity), !is.na(age)) %>% 
	group_by(age) %>% 
	summarize(avg_fam = mean(familiarity)) %>% 
	ggplot(aes(x = age, y = avg_fam)) +
	geom_hline(yintercept = avg_familiarity, linetype = 2) +
	geom_col() +
	coord_cartesian(ylim = c(0, 4)) +
	annotate(
		"text", 
		x = "45-49", 
		y = avg_familiarity, 
		label = "Average\nFamiliarity for All",
		hjust = 0,
		vjust = 0
	) +
	theme_minimal() +
  labs(
    title = "Average 311 Familiarity by Age",
    y = "Average Familiarity\n(from 0-4)",
    x = "Age",
    caption = "\nResponses only include those that passed our attention test."
  )
```

```{r, echo=FALSE}
total_pre_avg <-
	data %>% 
	summarize(
 		`Act. Noise Complaint` = mean(noise_complaint, na.rm = TRUE),
 		`Act. Graffiti Complaint` = mean(graffiti_complaint, na.rm = TRUE),
 		`Act. Roadway Complaint` = mean(roadway_complaint, na.rm = TRUE),
 		total_pre_avg = 
 			mean(
 				`Act. Noise Complaint`,
 				`Act. Graffiti Complaint`,
 				`Act. Roadway Complaint`
 			)
	) %>% 
	pull(total_pre_avg)

# Questions by Sex
data %>% 
	group_by(sex) %>% 
	summarize(
 		`Act. Noise Complaint` = mean(noise_complaint, na.rm = TRUE),
 		`Act. Graffiti Complaint` = mean(graffiti_complaint, na.rm = TRUE),
 		`Act. Roadway Complaint` = mean(roadway_complaint, na.rm = TRUE),
	) %>% 
	gather(
		key = "variable",
		value = "avg_response",
		starts_with("Act.")
	) %>% 
	ggplot(aes(x = sex, y = avg_response)) +
	geom_hline(aes(yintercept = total_pre_avg), linetype = 2) +
	geom_col() +
	coord_cartesian(ylim = c(0,5)) +
	facet_wrap(~variable, nrow = 1, ncol = 4) +
	theme_minimal() +
	labs(
    title = "Average Willingness to Make a Given Complaint via 311 by Sex",
    y = "Average Willingess to Make a Given Complaint\n(from 0-5)",
    x = "Sex",
    caption = "\nResponses are based on statistical adjustments."
  )

# Questions by Race
data %>% 
	group_by(race) %>% 
	summarize(
 		`Act. Noise Complaint` = mean(noise_complaint, na.rm = TRUE),
 		`Act. Graffiti Complaint` = mean(graffiti_complaint, na.rm = TRUE),
 		`Act. Roadway Complaint` = mean(roadway_complaint, na.rm = TRUE),
	) %>% 
	gather(
		key = "variable",
		value = "avg_response",
		starts_with("Act.")
	) %>% 
	ggplot(aes(x = fct_reorder(race, avg_response), y = avg_response)) +
	geom_hline(aes(yintercept = total_pre_avg), linetype = 2) +
	geom_col() +
	coord_cartesian(ylim = c(0,5)) +
	facet_wrap(~variable, nrow = 1, ncol = 4) +
	theme_minimal() +
	labs(
    title = "Average Willingness to Make a Given Complaint via 311 by Race",
    y = "Average Willingess to Make a Given Complaint\n(from 0-5)",
    x = "Race",
    caption = "\nResponses are based on statistical adjustments."
  )

# Questions by Education
data %>% 
	filter(!is.na(education)) %>% 
	group_by(education) %>% 
	summarize(
 		`Act. Noise Complaint` = mean(noise_complaint, na.rm = TRUE),
 		`Act. Graffiti Complaint` = mean(graffiti_complaint, na.rm = TRUE),
 		`Act. Roadway Complaint` = mean(roadway_complaint, na.rm = TRUE),
	) %>% 
	gather(
		key = "variable",
		value = "avg_response",
		starts_with("Act.")
	) %>% 
	ggplot(aes(x = education, y = avg_response)) +
	geom_hline(aes(yintercept = total_pre_avg), linetype = 2) +
	geom_col() +
	coord_cartesian(ylim = c(0,5)) +
	facet_wrap(~variable, nrow = 1, ncol = 4) +
	theme_minimal() +
	theme(
		axis.text.x.bottom = element_text(angle = 45, hjust = 1)
	) +
	labs(
    title = "Average Willingness to Make a Given Complaint via 311 by Education",
    y = "Average Willingess to Make a Given Complaint\n(from 0-5)",
    x = "Education",
    caption = "\nResponses are based on statistical adjustments."
  )

# Questions by Age
data %>% 
	filter(!is.na(age)) %>% 
	group_by(age) %>% 
	summarize(
 		`Act. Noise Complaint` = mean(noise_complaint, na.rm = TRUE),
 		`Act. Graffiti Complaint` = mean(graffiti_complaint, na.rm = TRUE),
 		`Act. Roadway Complaint` = mean(roadway_complaint, na.rm = TRUE),
	) %>% 
	gather(
		key = "variable",
		value = "avg_response",
		starts_with("Act.")
	) %>% 
	ggplot(aes(x = age, y = avg_response)) +
	geom_hline(aes(yintercept = total_pre_avg), linetype = 2) +
	geom_col() +
	coord_cartesian(ylim = c(0,5)) +
	facet_wrap(~variable, nrow = 1, ncol = 4) +
	theme_minimal() +
	theme(
		axis.text.x.bottom = element_text(angle = 45, hjust = 1)
	) +
	labs(
    title = "Average Willingness to Make a Given Complaint via 311 by Age",
    y = "Average Willingess to Make a Given Complaint\n(from 0-5)",
    x = "Age",
    caption = "\nResponses are based on statistical adjustments."
  )
```

```{r, include=FALSE}
## Statistical Adjustments
familiarity_model <- multinom(familiarity ~ sex + age + race + education, data = data)
noise_model <- multinom(noise_complaint ~ sex + age + race + education, data = data)
graffiti_model <- multinom(graffiti_complaint ~ sex + age + race + education, data = data)
roadway_model <- multinom(roadway_complaint ~ sex + age + race + education, data = data)
```

# Population Adjustments
```{r, echo=FALSE}
pop_est_all <-
	data_pop_distr %>% 
 	mutate(
		familiarity_preds = predict(familiarity_model, data_pop_distr) %>% as.integer(), 
		familiarity_preds = ifelse(familiarity_preds == 1, 0, familiarity_preds),
		noise_preds = predict(noise_model, data_pop_distr) %>% as.integer(),
 		graffiti_preds = predict(graffiti_model, data_pop_distr) %>% as.integer(),
 		roadway_preds = predict(roadway_model, data_pop_distr) %>% as.integer()
 	)
	
pop_est_table <-
	pop_est_all %>% 
	summarize(
 		`adj_fam` = weighted.mean(familiarity_preds, N),
 		`adj_noise` = weighted.mean(noise_preds, N),
 		`adj_graffiti` = weighted.mean(graffiti_preds, N),
 		`adj_roadway` = weighted.mean(roadway_preds, N)
 	)

adj_fam <- pop_est_table %>% pull(adj_fam)
adj_noise <- pop_est_table %>% pull(adj_noise)
adj_graffiti <- pop_est_table %>% pull(adj_graffiti)
adj_roadway <- pop_est_table %>% pull(adj_roadway)

avg_noise_complaint <- 
	data %>% 
	filter(attention == 4) %>% 
	pull(noise_complaint) %>% 
	mean(na.rm = TRUE)

avg_graffiti_complaint <- 
	data %>% 
	filter(attention == 4) %>% 
	pull(graffiti_complaint) %>% 
	mean(na.rm = TRUE)

avg_roadway_complaint <- 
	data %>% 
	filter(attention == 4) %>% 
	pull(roadway_complaint) %>% 
	mean(na.rm = TRUE)

tibble(
	Metric = c("311 Familiarity", "Willingness to Make a Noise Complaint", "Willingness to Make a Graffiti Complaint", "Willingness to Make a Roadway Complaint"),
	`Survey Value` = c(avg_familiarity, avg_noise_complaint, avg_graffiti_complaint, avg_roadway_complaint),
	`Population Adj. Value` = c(adj_fam, adj_noise, adj_graffiti, adj_roadway),
	Scale = c("0-4", "1-5", "1-5", "1-5")
)
```

Metric                                    |       Survey Value         | Population Adj. Value
----------------------------------------- | -------------------------- | ---------------------
311 Familiarity                           | `r avg_familiarity`        | `r adj_fam`
Willingness to Make a Noise Complaint     | `r avg_noise_complaint`    | `r adj_noise`
Willingness to Make a Graffiti Complaint  | `r avg_graffiti_complaint` | `r adj_graffiti`
Willingness to Make a Roadway Complaint   | `r avg_roadway_complaint`  | `r adj_roadway`

\newpage
# Analysis on Adjusted Data

\newpage
```{r, echo=FALSE}
# Adjusted Familiarity by Demographic Category

# Sex
pop_est_all %>% 
	group_by(sex) %>% 
	summarize(
		`Adj. Familiarity` = weighted.mean(familiarity_preds, N)
	) %>% 
	ggplot(aes(x = sex, y = `Adj. Familiarity`)) +
	geom_hline(aes(yintercept = c(2, 4)), linetype = 2) +
	geom_col() +
	annotate(
		"text", 
		x = "female", 
		y = c(2.2, 3.8),
		label = c("Somewhat Familiar", "Very Familiar"),
		hjust = 1
	) +
	coord_cartesian(ylim = c(0,4)) +
	theme_minimal() +
  labs(
    title = "Average 311 Familiarity by Sex",
    y = "Average Familiarity\n(from 0-4)",
    x = "Sex",
    caption = "\nResponses are based on statistical adjustments."
  )

# Race
pop_est_all %>% 
	group_by(race) %>% 
	summarize(
		`Adj. Familiarity` = weighted.mean(familiarity_preds, N)
	) %>% 
	ggplot(aes(x = race, y = `Adj. Familiarity`)) +
	geom_hline(aes(yintercept = c(2, 2, 4, 4)), linetype = 2) +
	geom_col() +
	annotate(
		"text", 
		x = "black", 
		y = c(2.2, 3.8),
		label = c("Somewhat Familiar", "Very Familiar"),
		hjust = 0
	) +
	coord_cartesian(ylim = c(0,4)) +
	theme_minimal() +
  labs(
    title = "Average 311 Familiarity by Race",
    y = "Average Familiarity\n(from 0-4)",
    x = "Race",
    caption = "\nResponses are based on statistical adjustments."
  )

# Education
pop_est_all %>% 
	group_by(education) %>% 
	summarize(
		`Adj. Familiarity` = weighted.mean(familiarity_preds, N)
	) %>% 
	mutate(
		education =
      factor(
        education,
        levels = c(
          "no high school diploma",
          "high school graduate",
          "college degree",
          "postgraduate degree"
        )
      )
	) %>% 
	ggplot(aes(x = education, y = `Adj. Familiarity`)) +
	geom_hline(aes(yintercept = c(2, 2, 4, 4)), linetype = 2) +
	geom_col() +
	annotate(
		"text",
		x = "no high school diploma",
		y = c(2.2, 3.8),
		label = c("Somewhat Familiar", "Very Familiar"),
		hjust = 0
	) +
	coord_cartesian(ylim = c(0,4)) +
	theme_minimal() +
  labs(
    title = "Average 311 Familiarity by Education",
    y = "Average Familiarity\n(from 0-4)",
    x = "Education",
    caption = "\nResponses are based on statistical adjustments."
  )

# Age
pop_est_all %>% 
	group_by(age) %>% 
	summarize(
		`Adj. Familiarity` = weighted.mean(familiarity_preds, N)
	) %>% 
	ggplot(aes(x = age, y = `Adj. Familiarity`)) +
	geom_hline(aes(yintercept = c(2, 2, 4, 4, 2, 2, 4, 4)), linetype = 2) +
	geom_col() +
	annotate(
		"text",
		x = "18-24",
		y = c(2.2, 3.8),
		label = c("Somewhat Familiar", "Very Familiar"),
		hjust = 0
	) +
	coord_cartesian(ylim = c(0,4)) +
	theme_minimal() +
  labs(
    title = "Average 311 Familiarity by Age",
    y = "Average Familiarity\n(from 0-4)",
    x = "Age",
    caption = "\nResponses are based on statistical adjustments."
  )
```

```{r, echo=FALSE}
total_avg <-
	pop_est_all %>% 
	summarize(
 		`Adj. Noise Complaint` = weighted.mean(noise_preds, N),
 		`Adj. Graffiti Complaint` = weighted.mean(graffiti_preds, N),
 		`Adj. Roadway Complaint` = weighted.mean(roadway_preds, N),
 		total_avg = 
 			mean(
 				`Adj. Noise Complaint`,
 				`Adj. Graffiti Complaint`,
 				`Adj. Roadway Complaint`
 			)
	) %>% 
	pull(total_avg)

# Adjusted Questions by Sex
pop_est_all %>% 
	group_by(sex) %>% 
	summarize(
 		`Adj. Noise Complaint` = weighted.mean(noise_preds, N),
 		`Adj. Graffiti Complaint` = weighted.mean(graffiti_preds, N),
 		`Adj. Roadway Complaint` = weighted.mean(roadway_preds, N)
	) %>% 
	gather(
		key = "variable",
		value = "avg_response",
		starts_with("Adj.")
	) %>% 
	ggplot(aes(x = sex, y = avg_response)) +
	geom_hline(aes(yintercept = total_avg), linetype = 2) +
	geom_col() +
	coord_cartesian(ylim = c(0,5)) +
	facet_wrap(~variable, nrow = 1, ncol = 4) +
	theme_minimal() +
	labs(
    title = "Average Willingness to Make a Given Complaint via 311 by Sex",
    y = "Average Willingess to Make a Given Complaint\n(from 0-5)",
    x = "Sex",
    caption = "\nResponses are based on statistical adjustments."
  )

# Adjusted Questions by Race
pop_est_all %>% 
	group_by(race) %>% 
	summarize(
 		`Adj. Noise Complaint` = weighted.mean(noise_preds, N),
 		`Adj. Graffiti Complaint` = weighted.mean(graffiti_preds, N),
 		`Adj. Roadway Complaint` = weighted.mean(roadway_preds, N)
	) %>% 
	gather(
		key = "variable",
		value = "avg_response",
		starts_with("Adj.")
	) %>% 
	ggplot(aes(x = fct_reorder(race, avg_response), y = avg_response)) +
	geom_hline(aes(yintercept = total_avg), linetype = 2) +
	geom_col() +
	coord_cartesian(ylim = c(0,5)) +
	facet_wrap(~variable, nrow = 1, ncol = 4) +
	theme_minimal() +
	labs(
    title = "Average Willingness to Make a Given Complaint via 311 by Race",
    y = "Average Willingess to Make a Given Complaint\n(from 0-5)",
    x = "Race",
    caption = "\nResponses are based on statistical adjustments."
  )

# Adjusted Questions by Education
pop_est_all %>% 
	group_by(education) %>% 
	summarize(
 		`Adj. Noise Complaint` = weighted.mean(noise_preds, N),
 		`Adj. Graffiti Complaint` = weighted.mean(graffiti_preds, N),
 		`Adj. Roadway Complaint` = weighted.mean(roadway_preds, N)
	) %>% 
	gather(
		key = "variable",
		value = "avg_response",
		starts_with("Adj.")
	) %>% 
	ggplot(aes(x = education, y = avg_response)) +
	geom_hline(aes(yintercept = total_avg), linetype = 2) +
	geom_col() +
	coord_cartesian(ylim = c(0,5)) +
	facet_wrap(~variable, nrow = 1, ncol = 4) +
	theme_minimal() +
	theme(
		axis.text.x.bottom = element_text(angle = 45, hjust = 1)
	) +
	labs(
    title = "Average Willingness to Make a Given Complaint via 311 by Education",
    y = "Average Willingess to Make a Given Complaint\n(from 0-5)",
    x = "Education",
    caption = "\nResponses are based on statistical adjustments."
  )

#Adjusted Questions by Age
pop_est_all %>% 
	group_by(age) %>% 
	summarize(
 		`Adj. Noise Complaint` = weighted.mean(noise_preds, N),
 		`Adj. Graffiti Complaint` = weighted.mean(graffiti_preds, N),
 		`Adj. Roadway Complaint` = weighted.mean(roadway_preds, N)
	) %>% 
	gather(
		key = "variable",
		value = "avg_response",
		starts_with("Adj.")
	) %>% 
	ggplot(aes(x = age, y = avg_response)) +
	geom_hline(aes(yintercept = total_avg), linetype = 2) +
	geom_col() +
	coord_cartesian(ylim = c(0,5)) +
	facet_wrap(~variable, nrow = 1, ncol = 4) +
	theme_minimal() +
	theme(
		axis.text.x.bottom = element_text(angle = 45, hjust = 1)
	) +
	labs(
    title = "Average Willingness to Make a Given Complaint via 311 by Age",
    y = "Average Willingess to Make a Given Complaint\n(from 0-5)",
    x = "Age",
    caption = "\nResponses are based on statistical adjustments."
  )
```

